---
title: "chapter6"
output: html_document
date: '2022-06-22'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)
```

# 6.3.2 R examples: Correlogram and simulation

The autocorrelation function for an MA(q) process (Equation (6.3)) can read-
ily be implemented in R, and a simple version, without any detailed error
checks, is given below. Note that the function takes the lag k and the model
parameters βi for i = 0, 1, . . . , q, with β0 = 1. For the non-zero values (i.e.,
values within the else part of the if-else statement), the autocorrelation
function is computed in two stages using a for loop. The first loop generates
a sum (s1) for the autocovariance, whilst the second loop generates a sum
(s2) for the variance, with the division of the two sums giving the returned
autocorrelation (ACF).


```{r pressure, echo=FALSE}

rho <- function(k, beta) {
  q <- length(beta) - 1
if (k > q) ACF <- 0 else {
    s1 <- 0; s2 <- 0
    for (i in 1:(q-k+1)) s1 <- s1 + beta[i] * beta[i+k]
    for (i in 1:(q+1)) s2 <- s2 + beta[i]^2
  ACF <- s1 / s2}
  ACF}

```


```{r}

beta <- c(1, 0.7, 0.5, 0.2)
rho.k <- rep(1, 10)
for (k in 1:10) 
{
  rho.k[k] <- rho(k, beta)
}
plot(0:10, c(1, rho.k), pch = 4, ylab = expression(rho[k]))
abline(0, 0)

```

```{r}

x.ma <- arima(x, order = c(0, 0, 3))
x.ma

```


```{r}

the_file = paste(directory,"/pounds_nz.dat",sep="")
Z <- read.table(the_file, header = T)
Z[1:4,]
Z.ts <- ts(Z, st = 1991, fr = 4)

x.ma <- arima(Z.ts, order = c(0, 0, 1))
x.ma

```

