---
title: "chapter11"
output: html_document
date: '2022-07-05'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)

```


11.2 -- Spurious Regression.

```{r}

the_file = paste(directory,"/cbe.dat",sep="")
CBE = read.table(the_file,header=T)

Elec.ts <- ts(CBE[, 3], start = 1958, freq = 12)
Choc.ts <- ts(CBE[, 1], start = 1958, freq = 12)

plot(as.vector(aggregate(Choc.ts)))
plot(aggregate(Elec.ts))
plot(as.vector(aggregate(Choc.ts)), aggregate(Elec.ts))


```





```{r}



```