---
title: "chapter2"
output: html_document
date: '2022-06-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)
```
# 2.2.1 Expected value

We now use R to calculate the covariance for the Herald Square pairs in
three different ways:


```{r pressure, echo=FALSE}
set.seed(1)
w <- rnorm(100)
plot(w, type = "l")
```


```{r pressure, echo=FALSE}
x <- seq(-3,3, length = 1000)
hist(rnorm(100), prob = T); points(x, dnorm(x), type = "l")
```


```{r pressure, echo=FALSE}
set.seed(2)
acf(rnorm(100))
```




```{r pressure, echo=FALSE}
#4.3.7 Simulation
#It is often helpful to study a time series model by simulation. This enables the
#main features of the model to be observed in plots, so that when historical data
#exhibit similar features, the model may be selected as a potential candidate.
#The following commands can be used to simulate random walk data for x:
x <- w <- rnorm(1000)
for (t in 2:1000) x[t] <- x[t - 1] + w[t]
plot(x, type = "l")
```






```{r pressure, echo=FALSE}
x <- seq(-3,3, length = 1000)
hist(rnorm(100), prob = T); points(x, dnorm(x), type = "l")
```




```{r pressure, echo=FALSE}
x <- seq(-3,3, length = 1000)
hist(rnorm(100), prob = T); points(x, dnorm(x), type = "l")
```
