---
title: "chapter5"
output: html_document
date: '2022-06-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse","patchwork")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
library(patchwork)

get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)
```
# 5.2.2 Stationarity


```{r pressure, echo=FALSE}
 set.seed(1)
 z <- w <- rnorm(100, sd = 20)
 for (t in 2:100) z[t] <- 0.8 * z[t - 1] + w[t]
 Time <- 1:100
 x <- 50 + 3 * Time + z
 plot(x, xlab = "time", type = "l")
```
The model for the code above can be expressed as xt = 50 + 3t + zt , where
{zt } is the AR(1) process zt = 0.8zt−1 + wt and {wt } is Gaussian white noise
with σ = 20. A time plot of a realisation of {xt } is given in Figure 5.1.


# Fitted models

```{r pressure, echo=FALSE}
x.lm <- lm(x ~ Time)
coef(x.lm)
sqrt(diag(vcov(x.lm)))
```


```{r pressure, echo=FALSE}
my_acf<-ggAcf(resid(x.lm)) 

my_pacf<-ggPacf(resid(x.lm))

my_acf/
  my_pacf

```

# 5.3.2 Model fitted to the temperature series (1970–2005)


```{r pressure, echo=FALSE}

global.dat <- read.table(fileandpath("global.dat"), header = T)


Global <- scan(fileandpath("global.dat"))
Global.ts <- ts(Global, st = c(1856, 1), end = c(2005,12), fr = 12)
temp <- window(Global.ts, start = 1970)
temp.lm <- lm(temp ~ time(temp))
coef(temp.lm)

time(temp)

 confint(temp.lm)

myacf <-ggAcf(resid(lm(temp ~ time(temp))))

myacf

```




# 5.4 Generalised least squares



```{r pressure, echo=FALSE}

list.of.packages <- c("nlme")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(nlme)



x.gls <- gls(x ~ Time, cor = corAR1(0.8))
coef(x.gls)
sqrt(diag(vcov(x.gls)))

```



# 5.4.2 Confidence interval for the trend in the temperature series



```{r pressure, echo=FALSE}

temp.gls <- gls(temp ~ time(temp), cor = corAR1(0.7))
confint(temp.gls)

```

# 5.5 Linear models with seasonal variables


```{r pressure, echo=FALSE}

temp.gls <- gls(temp ~ time(temp), cor = corAR1(0.7))
confint(temp.gls)

```


# 5.5.3 Example: Seasonal model for the temperature series

```{r pressure, echo=FALSE}

Seas <- cycle(temp)
Time <- time(temp)
temp.lm <- lm(temp ~ 0 + Time + factor(Seas))
coef(temp.lm)

```



```{r pressure, echo=FALSE}

new.t <- seq(2006, len = 2 * 12, by = 1/12)
alpha <- coef(temp.lm)[1]
beta <- rep(coef(temp.lm)[2:13], 2)
(alpha * new.t + beta)[1:4]

```



```{r pressure, echo=FALSE}

new.dat <- data.frame(Time = new.t, Seas = rep(1:12, 2))
predict(temp.lm, new.dat)[1:24]

```

# 5.7 Logarithmic transformations

# 5.7.2 Example using the air passenger series


```{r pressure, echo=FALSE}

data(AirPassengers)
AP <- AirPassengers
plot(AP)
plot(log(AP))

```

```{r}


SIN <- COS <- matrix(nr = length(AP), nc = 6)
 for (i in 1:6) {
SIN[, i] <- sin(2 * pi * i * time(AP))
COS[, i] <- cos(2 * pi * i * time(AP))
}
TIME <- (time(AP) - mean(time(AP)))/sd(time(AP))
mean(time(AP))

sd(time(AP))

AP.lm1 <- lm(log(AP) ~ TIME + I(TIME^2) + I(TIME^3) + I(TIME^4) +
SIN[,1] + COS[,1] + SIN[,2] + COS[,2] + SIN[,3] + COS[,3] +
SIN[,4] + COS[,4] + SIN[,5] + COS[,5] + SIN[,6] + COS[,6])
coef(AP.lm1)/sqrt(diag(vcov(AP.lm1)))

AP.lm2 <- lm(log(AP) ~ TIME + I(TIME^2) + SIN[,1] + COS[,1] +
SIN[,2] + COS[,2] + SIN[,3] + SIN[,4] + COS[,4] + SIN[,5])
coef(AP.lm2)/sqrt(diag(vcov(AP.lm2)))

AIC(AP.lm1)
AIC(AP.lm2)

```

```{r}
acf1 <- ggAcf(resid(AP.lm1))
acf2 <- ggPacf(resid(AP.lm1))


acf1 / 
  acf2

```


```{r}

AP.gls <- gls(log(AP) ~ TIME + I(TIME^2) + SIN[,1] + COS[,1] +
SIN[,2] + COS[,2] + SIN[,3] + SIN[,4] + COS[,4] + SIN[,5],
cor = corAR1(0.6))
coef(AP.gls)/sqrt(diag(vcov(AP.gls)))

AP.ar <- ar(resid(AP.lm2), order = 1, method = "mle")
AP.ar$ar


```
```{r}

 ggAcf(AP.ar$res[-1])

```

# 5.8.2 Example of a simulated and fitted non-linear series

```{r}

 set.seed(1)
 w <- rnorm(100, sd = 10)
 z <- rep(0, 100)
 for (t in 2:100) z[t] <- 0.7 * z[t - 1] + w[t]
 Time <- 1:100
 f <- function(x) exp(1 + 0.05 * x)
 x <- f(Time) + z
 plot(x, type = "l")
 abline(0, 0)

```



```{r}

x.nls <- nls(x ~ exp(alp0 + alp1 * Time), start = list(alp0 = 0.1, alp1 = 0.5))
summary(x.nls)$parameters

```



```{r}

new.t <- time(ts(start = 1961, end = c(1970, 12), fr = 12))
TIME <- (new.t - mean(time(AP)))/sd(time(AP))
SIN <- COS <- matrix(nr = length(new.t), nc = 6)
for (i in 1:6) {
COS[, i] <- cos(2 * pi * i * new.t)
SIN[, i] <- sin(2 * pi * i * new.t)
}
SIN <- SIN[, -6]
new.dat <- data.frame(TIME = as.vector(TIME), SIN = SIN,
COS = COS)
AP.pred.ts <- exp(ts(predict(AP.lm2, new.dat), st = 1961,
fr = 12))
ts.plot(log(AP), log(AP.pred.ts), lty = 1:2)
ts.plot(AP, AP.pred.ts, lty = 1:2)


```

# 5.10 Inverse transform and bias correction

## 5.10.1 Log-normal residual errors



```{r}

set.seed(1)
sigma <- 1
w <- rnorm(1e+06, sd = sigma)
mean(w)
mean(exp(w))
exp(sigma^2/2)
```


## 5.10.2 Empirical correction factor for forecasting means
## 5.10.3 Example using the air passenger data

```{r}

summary(AP.lm2)$r.sq

sigma <- summary(AP.lm2)$sigma
lognorm.correction.factor <- exp((1/2) * sigma^2)
empirical.correction.factor <- mean(exp(resid(AP.lm2)))
lognorm.correction.factor
empirical.correction.factor
AP.pred.ts1 <- AP.pred.ts * empirical.correction.factor

```
```{r}

autoplot(AP.pred.ts1)

```

```{r}

autoplot(AP.pred.ts)

```