---
title: "chapter6"
output: html_document
date: '2022-06-22'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)
```
# 2.2.1 Expected value

We now use R to calculate the covariance for the Herald Square pairs in
three different ways:


```{r pressure, echo=FALSE}
set.seed(1)
w <- rnorm(100)
plot(w, type = "l")
```


```{r pressure, echo=FALSE}
x <- seq(-3,3, length = 1000)
hist(rnorm(100), prob = T); points(x, dnorm(x), type = "l")
```


```{r pressure, echo=FALSE}
set.seed(2)
acf(rnorm(100))
```




```{r pressure, echo=FALSE}
#4.3.7 Simulation
#It is often helpful to study a time series model by simulation. This enables the
#main features of the model to be observed in plots, so that when historical data
#exhibit similar features, the model may be selected as a potential candidate.
#The following commands can be used to simulate random walk data for x:
x <- w <- rnorm(1000)
for (t in 2:1000) x[t] <- x[t - 1] + w[t]
plot(x, type = "l")
```



```{r pressure, echo=FALSE}
x <- seq(-3,3, length = 1000)
hist(rnorm(100), prob = T); points(x, dnorm(x), type = "l")
```



```{r pressure, echo=FALSE}
x <- seq(-3,3, length = 1000)
hist(rnorm(100), prob = T); points(x, dnorm(x), type = "l")
```


# 4.5.5 Correlogram of an AR(1) process

```{r}

rho <- function(k, alpha) alpha^k
 layout(1:2)
 plot(0:10, rho(0:10, 0.7), type = "b")
 plot(0:10, rho(0:10, -0.7), type = "b")
 
```

```{r}

rho <- function(k, alpha) alpha^k
 layout(1:2)
 plot(0:10, rho(0:10, 0.1), type = "b")
 plot(0:10, rho(0:10, 2), type = "b")
  plot(0:10, rho(0:10, 0.2), type = "b")
 plot(0:10, rho(0:10, -.3), type = "b")
 
```

#4.5.7 Simulation

An AR(1) process can be simulated in R as follows:


```{r}

set.seed(1)
x <- w <- rnorm(100)
for (t in 2:100) x[t] <- 0.7 * x[t - 1] + w[t]
plot(x, type = "l")
acf(x)
pacf(x)
```


#4.6 Fitted models
##4.6.1 Model fitted to simulated series

```{r}

x.ar <- ar(x, method = "mle")
print(x.ar$order)
print(x.ar$ar)
print(x.ar$ar + c(-2, 2) * sqrt(x.ar$asy.var))

```



```{r}

the_file = paste(directory,"/pounds_nz.dat",sep="")
Z <- read.table(the_file, header = T)
Z[1:4,]
Z.ts <- ts(Z, st = 1991, fr = 4)

Z.ar <- ar(Z.ts)
mean(Z.ts)
print(Z.ar$order)
print(Z.ar$ar)
print(Z.ar$ar + c(-2, 2) * sqrt(Z.ar$asy.var))

acf(Z.ar$res[-1])

```




```{r}

the_file = paste(directory,"/global.dat",sep="")
Global = scan(the_file)
Global.ts = ts(Global, st = c(1856, 1), end = c(2005, 12), fr = 12)

Global.ar <- ar(aggregate(Global.ts, FUN = mean), method = "mle")
print( mean(aggregate(Global.ts, FUN = mean)))
#[1] -0.1383
print( Global.ar$order)
print(Global.ar$ar)

#[1] 0.58762 0.01260 0.11117 0.26764
#−0.2
#0.2
acf(Global.ar$res[-(1:Global.ar$order)], lag = 50)


```


```{r}



```


```{r}


```