---
title: "chapter11"
output: html_document
date: '2022-07-05'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse","mvtnorm","vars")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)

```


11.2 -- Spurious Regression.

```{r}

the_file = paste(directory,"/cbe.dat",sep="")
CBE = read.table(the_file,header=T)

Elec.ts <- ts(CBE[, 3], start = 1958, freq = 12)
Choc.ts <- ts(CBE[, 1], start = 1958, freq = 12)

plot(as.vector(aggregate(Choc.ts)))
plot(aggregate(Elec.ts))
plot(as.vector(aggregate(Choc.ts)), aggregate(Elec.ts))
cor(aggregate(Choc.ts), aggregate(Elec.ts))

```


```{r}

set.seed(10); x <- rnorm(100); y <- rnorm(100)
for(i in 2:100) {
x[i] <- x[i-1] + rnorm(1)
y[i] <- y[i-1] + rnorm(1) }
plot(x, y)
cor(x, y)

```

```{r}

the_file = paste(directory,"/us_rates.dat",sep="")
xrates = read.table(the_file,header=T)

xrates[1:3, ]

acf( diff(xrates$UK) )
acf( diff(xrates$EU) )
plot(xrates$UK, xrates$EU, pch = 4)
cor(xrates$UK, xrates$EU)

```



11.3 Test for unit roots:


```{r}

library(tseries)

adf.test(x)

```

```{r}

pp.test(xrates$UK)

pp.test(xrates$EU)


```


```{r}

 x <- y <- mu <- rep(0, 1000)
 for (i in 2:1000) mu[i] <- mu[i - 1] + rnorm(1)
 x <- mu + rnorm(1000)
 y <- mu + rnorm(1000)
 adf.test(x)$p.value

 adf.test(y)$p.value

 po.test(cbind(x, y))

 
```


```{r}

po.test(cbind(xrates$UK, xrates$EU))

ukeu.lm <- lm(xrates$UK ~ xrates$EU)
ukeu.res <- resid(ukeu.lm)
ukeu.res.ar <- ar(ukeu.res)
ukeu.res.ar$order

AIC(arima(ukeu.res, order = c(3, 0, 0)))

AIC(arima(ukeu.res, order = c(2, 0, 0)))

AIC(arima(ukeu.res, order = c(1, 0, 0)))

AIC(arima(ukeu.res, order = c(1, 1, 0)))

```

### 11.5 Bivariate and multivariate white noise


```{r}

library(mvtnorm)
cov.mat <- matrix(c(1, 0.8, 0.8, 1), nr = 2)
w <- rmvnorm(1000, sigma = cov.mat)
cov(w)

wx <- w[, 1]
wy <- w[, 2]
ccf(wx, wy, main = "")

```



```{r}

Mod(polyroot(c(1, -0.5, -0.02)))

```


```{r}

 x <- y <- rep(0, 1000)
 x[1] <- wx[1]
 y[1] <- wy[1]
 for (i in 2:1000) {

x[i] <- 0.4 * x[i - 1] + 0.3 * y[i - 1] + wx[i]
y[i] <- 0.2 * x[i - 1] + 0.1 * y[i - 1] + wy[i]
}
 xy.ar <- ar(cbind(x, y))
 xy.ar$ar[, , ]

```

## 11.6.1 VAR model fitted to US economic series

```{r}

library(tseries)
data(USeconomic)
US.ar <- ar(cbind(GNP, M1), method="ols", dmean=T, intercept=F)
US.ar$ar

```

```{r}
acf(US.ar$res[-c(1:3), 1])
acf(US.ar$res[-c(1:3), 2])
```



```{r}

library(vars)
US.var <- VAR(cbind(GNP, M1), p = 3, type = "trend")
coef(US.var)

```

```{r}

US.var <- VAR(cbind(GNP, M1), p = 2, type = "trend")
coef(US.var)

```



```{r}

acf(resid(US.var)[, 1])
acf(resid(US.var)[, 2])

```


```{r}

US.pred <- predict(US.var, n.ahead = 4)
US.pred
 

```



```{r}

GNP.pred <- ts(US.pred$fcst$GNP[, 1], st = 1988, fr = 4)
M1.pred <- ts(US.pred$fcst$M1[, 1], st = 1988, fr = 4)
ts.plot(cbind(window(GNP, start = 1981), GNP.pred), lty = 1:2)
ts.plot(cbind(window(M1, start = 1981), M1.pred), lty = 1:2)


```

