---
title: "chapter7"
output: html_document
date: '2022-07-02'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)

```
```{r}
#Differencing and the electrical series.

the_file = paste(directory,"/cbe.dat",sep="")
CBE <- read.table(the_file, he=T)
Elec.ts <- ts(CBE[, 3], start = 1958, freq = 12)
layout(c(1, 1, 2, 3))
plot(Elec.ts)
plot(diff(Elec.ts))
plot(diff(log(Elec.ts)))



```




```{r}

 set.seed(1)
 x <- w <- rnorm(1000)
 for (i in 3:1000) x[i] <- 0.5 * x[i - 1] + x[i - 1] - 0.5 *
x[i - 2] + w[i] + 0.3 * w[i - 1]
 arima(x, order = c(1, 1, 1))

```


```{r}

x <- arima.sim(model = list(order = c(1, 1, 1), ar = 0.5,
ma = 0.3), n = 1000)
arima(x, order = c(1, 1, 1))

```


```{r}

the_file = paste(directory,"/cbe.dat",sep="")
CBE = read.table(the_file,header=T)

Beer.ts <- ts(CBE[, 2], start = 1958, freq = 12)
Beer.ima <- arima(Beer.ts, order = c(0, 1, 1))
Beer.ima

```
```{r}
acf(resid(Beer.ima))

```


```{r}
Beer.1991 <- predict(Beer.ima, n.ahead = 12)
sum(Beer.1991$pred)

```



```{r}

Elec.ts <- ts(CBE[, 3], start = 1958, freq = 12)
 AIC (arima(log(Elec.ts), order = c(1,1,0),
seas = list(order = c(1,0,0), 12)))

 AIC (arima(log(Elec.ts), order = c(0,1,1),
seas = list(order = c(0,0,1), 12)))

```


```{r}

get.best.arima <- function(x.ts, maxord = c(1,1,1,1,1,1))
{
best.aic <- 1e8
n <- length(x.ts)
for (p in 0:maxord[1]) for(d in 0:maxord[2]) for(q in 0:maxord[3])
for (P in 0:maxord[4]) for(D in 0:maxord[5]) for(Q in 0:maxord[6])
{
fit <- arima(x.ts, order = c(p,d,q),
seas = list(order = c(P,D,Q),
frequency(x.ts)), method = "CSS")
fit.aic <- -2 * fit$loglik + (log(n) + 1) * length(fit$coef)
if (fit.aic < best.aic)
best.aic <- fit.aic
best.fit <- fit
best.model <- c(p,d,q,P,D,Q)
}
}
list(best.aic, best.fit, best.model)
}
 best.arima.elec <- get.best.arima( log(Elec.ts),
maxord = c(2,2,2,2,2,2))
best.fit.elec <- best.arima.elec[[2]]
acf( resid(best.fit.elec) )

best.arima.elec [[3]]

ts.plot( cbind( window(Elec.ts,start = 1981), exp(predict(best.fit.elec,12)$pred) ), lty = 1:2)


```


