---
title: "chapter11"
output: html_document
date: '2022-07-05'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#```{r setup echo=FALSE, message=FALSE, warnings=FALSE}
```{r setup }
list.of.packages <- c("rstudioapi","tidyverse","mvtnorm")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(rstudioapi)
library(tidyverse)
get_my_wd <- function()
{
  current_doc <- getActiveDocumentContext()$path 
  current_path <- str_replace(str_replace(paste(gsub("(.*)/.*","\\1",current_doc),"")," ",""), " ","")
  return(current_path)
}

directory <-get_my_wd()

r_file = paste(directory,"/functions.R",sep="")
print(get_my_wd())
print(r_file)

source(r_file)

```


11.2 -- Spurious Regression.

```{r}

the_file = paste(directory,"/cbe.dat",sep="")
CBE = read.table(the_file,header=T)

Elec.ts <- ts(CBE[, 3], start = 1958, freq = 12)
Choc.ts <- ts(CBE[, 1], start = 1958, freq = 12)

plot(as.vector(aggregate(Choc.ts)))
plot(aggregate(Elec.ts))
plot(as.vector(aggregate(Choc.ts)), aggregate(Elec.ts))
cor(aggregate(Choc.ts), aggregate(Elec.ts))

```


```{r}

set.seed(10); x <- rnorm(100); y <- rnorm(100)
for(i in 2:100) {
x[i] <- x[i-1] + rnorm(1)
y[i] <- y[i-1] + rnorm(1) }
plot(x, y)
cor(x, y)

```

```{r}

the_file = paste(directory,"/us_rates.dat",sep="")
xrates = read.table(the_file,header=T)

xrates[1:3, ]

acf( diff(xrates$UK) )
acf( diff(xrates$EU) )
plot(xrates$UK, xrates$EU, pch = 4)
cor(xrates$UK, xrates$EU)

```



11.3 Test for unit roots:


```{r}

library(tseries)

adf.test(x)

```

```{r}

pp.test(xrates$UK)

pp.test(xrates$EU)


```


```{r}

 x <- y <- mu <- rep(0, 1000)
 for (i in 2:1000) mu[i] <- mu[i - 1] + rnorm(1)
 x <- mu + rnorm(1000)
 y <- mu + rnorm(1000)
 adf.test(x)$p.value

 adf.test(y)$p.value

 po.test(cbind(x, y))

 
```


```{r}

po.test(cbind(xrates$UK, xrates$EU))

ukeu.lm <- lm(xrates$UK ~ xrates$EU)
ukeu.res <- resid(ukeu.lm)
ukeu.res.ar <- ar(ukeu.res)
ukeu.res.ar$order

AIC(arima(ukeu.res, order = c(3, 0, 0)))

AIC(arima(ukeu.res, order = c(2, 0, 0)))

AIC(arima(ukeu.res, order = c(1, 0, 0)))

AIC(arima(ukeu.res, order = c(1, 1, 0)))

```

### 11.5 Bivariate and multivariate white noise


```{r}

library(mvtnorm)
cov.mat <- matrix(c(1, 0.8, 0.8, 1), nr = 2)
w <- rmvnorm(1000, sigma = cov.mat)
cov(w)

wx <- w[, 1]
wy <- w[, 2]
ccf(wx, wy, main = "")

```



